Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-18 doc/RMD/locus-stats.Rmd
Clean out a lot of old results
There were extra figures and tables littering the
results directory due to various things including
misspelling. These have been cleared.

```{r load_packages, message = FALSE, warning = FALSE}
library("tidyverse")
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
```

>>>>

```{r load_packages, message = FALSE, warning = FALSE}
library("tidyverse")
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
dir.create(file.path(PROJHOME, "results", "tables"))
```

### 2017-08-18 doc/manuscript/manuscript.Rmd
Clean out a lot of old results
There were extra figures and tables littering the
results directory due to various things including
misspelling. These have been cleared.

prettify <- function(x, i) signif((1 - x[i])*100, 3)
paxis <- function(d, i = 1 ){
  res <- cumsum(d$eig)/sum(d$eig)
  prettify(res, i)
}
passp <- function(d, i = 1){
  res <- apply(d$posterior, 2, mean, na.rm = TRUE)
  prettify(1 - res, i)
}
```

>>>>

# convert fractions to percents with 3 sig figs
prettify <- function(x, i) signif((x[i])*100, 3)

# Get proportion of variance per discriminant axis
paxis <- function(d, i = 1){
  res <- cumsum(d$eig)/sum(d$eig)
  prettify(1 - res, i)
}

# Get proportion of assignment probability for a given population
passp <- function(d, i = 1){
  res <- apply(d$posterior, 2, mean, na.rm = TRUE)
  prettify(res, i)
}
```
